Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
another fix

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
benchmark~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches may improve fault localization up to $73.7\%$
(\avgImprov\ on average).\Mar{do we have supporting data to say that
  the improvement is bigger when we care the most? for the cases SFL
  performs worse? if yes, can we show average for that?} To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.

@@

As to quantify complexity of fault localization on this benchmark, we
counted the number of cases of ``fault of omission'', a popular metric
in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441}.  A fault of omission
(\foo) occurs when the program is buggy because some code is missing,
i.e., a fix to the bug iss created by adding code as opposed to
modifying or changing code. Intuitively, the ability of techniques to
produce accurate diagnostic reports in those cases might be poor as
techniques can only extract information about existing statements,
which are not problematic. This dataset has a total of $59.7\%$ of
\foo s, making it challenging for techniques to perform
well. \Mar{Sofia, does it make sense to show a histogram of (initial)
  rankings of pure SFL to complement this argument? Say, frequency of
  cases SFL reports on <top-10 statements in the ranking, then
  frequency within top-10> and <top-20, etc.}

@@

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of
      the variants (right)\Mar{por favor, aumente o tamanho dos labels
      (nao consigo enxergar na impressao).}}
		\label{fig:boxplot}
		\vspace{-0.2cm}

>>>>

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
benchmark~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in $9\%$\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches may improve fault localization up to $73.7\%$
(\avgImprov\ on average). To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring; and, the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.
% \Mar{do we have supporting data to say that
%   the improvement is bigger when we care the most? for the cases SFL
%   performs worse? if yes, can we show average for that?}

@@

As to quantify complexity of fault localization on this benchmark, we
counted the number of cases of ``fault of omission'', a popular metric
in fault localization research for that
purpose~\cite{Pearson:2017:EIF:3097368.3097441}.  A fault of omission
(\foo) occurs when the program is buggy because some code is missing,
i.e., a fix to the bug iss created by adding code as opposed to
modifying or changing code. Intuitively, the ability of techniques to
produce accurate diagnostic reports in those cases might be poor as
techniques can only extract information about existing statements,
which are not problematic. This dataset has a total of $59.7\%$ of
\foo s, making it challenging for techniques to perform
well.

% \Mar{Sofia, does it make sense to show a histogram of (initial)
%   rankings of pure SFL to complement this argument? Say, frequency of
%   cases SFL reports on <top-10 statements in the ranking, then
%   frequency within top-10> and <top-20, etc.}

@@

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of
      the variants (right)}
		\label{fig:boxplot}
		\vspace{-0.2cm}
